### 2022-11-03 files/Chapter3/dynamicconvergence.tex
adding to chapter 3

\subsection{Obtaining the error estimate}
In this section we will show how the error estimate in Theorem 2 is obtained in \cite{BV13}.\\

The following two assumptions are made in \cite{BV13}.

@@

\newtheorem{lem_1}{Lemma}
\begin{lem_1}
	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
	\begin{eqnarray}
		\Vert e(t)\Vert_{W} \leq \sqrt{2} \left( \Vert e(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \right).
	\end{eqnarray}
\end{lem_1}

@@

\newtheorem{col_1}{Corollary}
\begin{col_1}
	If $u$ is the solution of Problem GVar with $a = 0$ and $u$ satisfies assumption \textbf{B1}, then
	\begin{eqnarray}
		\Vert e(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
	\end{eqnarray}
\end{col_1}

\subsection{Semi-discrete problem}

>>>>

\subsection{Obtaining the error estimate}
In this section we will show how the error estimate in Theorem 2 is obtained in \cite{BV13}.The following two assumptions are made in \cite{BV13}.

@@

\newtheorem{lem_1}{Lemma}
\begin{lem_1}
	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
	\begin{eqnarray}
		\Vert e(t)\Vert_{W} &\leq& \sqrt{2} \biggl( \Vert e(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W\nonumber \\ 
		&& + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \biggr). \label{fundamental_estimate}
	\end{eqnarray}
\end{lem_1}

@@

\newtheorem{col_1}{Corollary}
\begin{col_1}
	If $u$ is the solution of Problem GVar with $a = 0$ and $u$ satisfies assumption \textbf{B1}, then
	\begin{eqnarray}
		\Vert e(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 2T||e'_h(0)||_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
	\end{eqnarray}
\end{col_1}

\subsubsection{Semi-discrete problem}
The estimate \eqref{fundamental_estimate} in Lemma 1 is equivalent to
\begin{eqnarray*}
	\Vert u(t) - u_h(t) \Vert_{W} &\leq& \sqrt{2} \biggl( \Vert u(0) - u_h(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W\nonumber \\ 
	&& + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \biggr).
\end{eqnarray*}
